Does at-issueness predict projection? Further investigations of the Gradient Projection Principle

### 2023-03-15 writing/SuB-abstract/SuB-abstract.tex
abstract submitted

% 1
\vspace{-.7\baselineskip}
\noindent 
	We present experimental data that the projection of the content of attitude complements \textbf{(i)} varies between entailment-canceling operators, and \textbf{(ii)} that this by-operator variation differs between attitude predicates.
	%
	The observed variability is not captured by existing theoretical accounts of projection
	(e.g., \citealt{heim_projection_1983,van_der_sandt_presupposition_1992,abrusan_predicting_2011,schlenker_triggering_2021}).
	%
	Our results suggest that an analysis must consider interactions between predicates and operators, which cannot be fully determined by lexical classes, instead revealing a more nuanced picture of lexical semantic and pragmatic properties. This raises important questions for future research on projection.
	%

% 2
\noindent {\bf Projection across entailment-cancelling operators.}
	Language users may infer that a speaker who utters an attitude ascription, as in \ref{ex:family}, is committed to the content of the complement (CC, here: \emph{Julian dances salsa,})
	even when it occurs under an entailment-canceling operator, like negation \ref{ex:neg}, polar questions \ref{ex:q}, modals \ref{ex:mod}, or conditionals \ref{ex:cond}, in which case we say that it \emph{projects}.

@@

	\vspace{-.5\baselineskip}
	\noindent  Current research rarely examines projection variability across these operators, with conflicting findings.
	%
	\citet{karttunen_observations_1971} proposed a distinction between English factive predicates (e.g., \emph{be annoyed, regret}), where the CC projects across all four operators, and semi-factives (e.g., \emph{discover, realize, see, notice}) where it always projects across negation, but not always for the other operators.
	%
	Comparing different types of contents, \citet{smith_relationship_2014} found that the projective content of epithets and the CC of \emph{know} was more projective under negation than conditionals,
	whereas that of non-restrictive relative clauses and \emph{win} showed the opposite pattern.
	%
	\posscite{sieker_projective_2022} study on German attitude predicates replicated \posscite{smith_relationship_2014} result for German \emph{wissen} (`know'), but as part of an overall pattern of higher projectivity across negation than other operators. They found no interaction with predicate type, or evidence for the (semi-)factive distinction.

	These studies yield divergent results regarding whether they find interactions between operators and various projective contents, therefore raising the question if this is due to cross-linguistic variation, task differences, or different contents being tested. To address this, we conducted a series of experiments designed to assess projection across the four entailment-canceling operators in \ref{ex:family}. We used the same projection measure as \citet{sieker_projective_2022} (the `certain that' diagnostic; see e.g., \citealp{tonhauser_how_2018,djarv_prosodic_2017,mahler_social_2020}) and applied it to the CC of 20 English clause-embedding predicates, including purported factive (\emph{be annoyed, know, reveal}) and semi-factive predicates (\emph{discover, see}),
	and 15 non-factive predicates, given recent findings that their complements are also projective, albeit to varying degrees (\citealt{degen_are_2022}).

@@

\noindent
{\bf Results and Analysis.} 
	%
	Our first key finding is that there is projection variability by operator: Across predicates, projection ratings were higher under question-embeddings than under negation and modals, but lower than in conditional antecedents. These differences, though small, are significant and supported by linear mixed effects model \textbf{\# 1} in \textbf{Table\ \ref{t:models}}. 
	%
	Second, there is by-predicate variation in the effect of operator on projection. This is illustrated in \textbf{Figure~\ref{fig:figure1}}, which shows mean projection ratings for the 20 attitude predicates by operator; predicates are ordered by their mean rating across all operators (\emph{be annoyed} has the highest overall mean).
	%
	For instance, whereas the CC of \emph{be annoyed} projects more from under negation (and questions) than conditionals and modals, the CC of \emph{know} projects less from under negation than questions, but more from under negation than modals, and the CC of \emph{discover} projects less from negation than conditionals and questions, and more from under negation than modals. This finding is further supported by models \textbf{\# 2--4} in \textbf{Table\ \ref{t:models}} each having at least $34$ significant interaction terms (out of $57$ possible interactions of \texttt{operator} and \texttt{predicate}).
	%
	% The models in \textbf{Table\ \ref{t:models}} also illustrate some specific differences across predicates in by-operator variation (using different reference levels for \texttt{predicate}): For instance, the CC of \emph{be annoyed} projects more from under negation (and questions) than conditionals and modals, while the CC of \emph{discover} projects less from negation than conditionals and questions, and more from under negation than modals.
	%
	%
	Contrary to what would be expected based on \posscite{karttunen_observations_1971}
	distinction between factive and semi-factive predicates,
	% the CC of assumed semi-factives \emph{discover, see} does not have higher projection-ratings under negation than other operators. \textbf{Figure~\ref{fig:figure1}} clearly shows that mean certainty ratings are lower for negation than conditionals and questions.
	%
	the CC of (factive) \emph{be annoyed} does not project invariably from all four operators, and the CC \emph{discover,}  which is considered semi-factive, does not project more from under negation than the other three operators. The pattern we observed for {\em know} does not fit into either category.
	%
	%
	Our findings, that by-operator projection variability differs by content, are in line with \citet{smith_relationship_2014}, but contrary to their findings that the CC of \emph{know} projects more from negation than conditionals, we found no significant difference here (Model \textbf{\# 4} in \textbf{Table\ \ref{t:models}}).\\

	%
	\noindent{\bf LH:} Alternatively, we might only talk about the missed predictions for the semi-factives here? \\

	\noindent Instead, we found that it projects less from under negation than questions, but more from under negation than modals, while the difference between negation and conditionals is not significant here.\\
	%
	%

	Like in \posscite{sieker_projective_2022} study of German attitude predicates, we find a presence of a main effect of by-operator projection variation, but the particular effect we find is different: While Sieker and Solstad found highest projection ratings with negation compared to the other operators, we find overall highest projectivity across conditionals, then questions, then modals and negation.
	%
	With many interaction effects of \texttt{operator} and \texttt{predicate} throughout, our results also differ from , who did not find such interactions for the German attitudes they investigated.
	%
	Since our study used the same projection diagnostic, and a similar set of contents as \cite{sieker_projective_2022}, the different results indicate potential cross-linguistic variation in projection variability. This suggests 
	extending the questions addressed in cross-linguistic investigations of projective variability (\citealt{tonhauser_projection_2020,xue_correlation_2011,tonhauser_how_2018}) to interactions with various entailment-cancelling operators.

	% \vspace{-.3\baselineskip}
	% \textbf{version w baseline know/m}
	% \noindent The data was analyzed using a mixed effects linear regression (using \texttt{lme4, lmertest} in \texttt{R}; \citealp{bates_fitting_2015,kuznetsova_lmertest_2016,r_core_team_r_2014}), with \texttt{know} and \texttt{modal} as reference levels, and random intercepts for participants and items. We found highly significant main effects of \texttt{operator} (\texttt{conditional}: $+0.142$, \texttt{negation}: $+0.143$, ; \texttt{question}: $+0.225$, where $p < 2e^{-16}$ in all three cases), as well as many interactions of \texttt{operator} and  \texttt{verb} across the board (where $p < 0.001$ in $38$ cases, $p < 0.01$ in one, and $p < 0.05$ in three out of $57$ possible interactions).\\

	%	\noindent The data was analyzed using a mixed effects linear regression (using \texttt{lme4, lmertest} in \texttt{R}; \citealp{bates_fitting_2015,kuznetsova_lmertest_2016,r_core_team_r_2014}), with \texttt{be\_annoyed} and \texttt{negation} as reference levels, and random intercepts for participants and items.
		% The mean for this baseline (intercept) is $0.867$.
	%	We found highly significant main effects of \texttt{operator}: For our baseline \texttt{be\_annoyed}, both \texttt{conditional} and \texttt{modal} are clearly less projective than negation, thereby supporting the claim that the embedding context does matter. We also found many interactions of \texttt{operator} and \texttt{verb} across the board, suggesting that the effect of embedding context diffes by verb. Notably, \emph{\lq discover\rq} is more projective in polar questions and conditional antecedents than under negation, patterning opposite to Karttunen's claims about semi-factives. For the emotive predicate \emph{\lq be annoyed\rq} no significant effect is found for \texttt{question} (vs \texttt{negation}), as would be expected based on Karttunen, but we do find unexpected differences between \texttt{negation} $>$ \texttt{conditional, modal}. \emph{know} shows effects that would be incompatible with a characterization as either factive or semi-factive: $\texttt{question} > \texttt{conditional, negation} > \texttt{modal}$. If \emph{\lq know\rq} is a factive predicate, no difference would be expected. If it is semi-factive, we would, again, expect higher projectivity under negation than in questions and conditionals.

	% for \texttt{conditional} ($-0.116$, $p < 1.6e^{-13}$) and \texttt{modal} ($-0.156$, $p < 2e^{-16}$), while the effect of \texttt{question} was only marginally significant ($+0.025$, $p < 0.1$). We also found many interactions of \texttt{operator} and \texttt{verb} across the board (where $p < 0.001$ in $43$ cases, $p < 0.01$ in three, and $p < 0.05$ in one out of $57$ possible interactions).\\

@@

{\bf Discussion.}
	Our results---that projection is modulated by entailment-canceling operators and that there is by-predicate variation in the effect of operator on projection---are not captured by contemporary projection analyses, for several reasons.
	%
	The first reason is that contemporary analyses do not lead us to expect interactions with different types of entailment-cancelling operators. In \citealt{heim_projection_1983}, for instance, the CC of (semi-)factive predicates projects to the global context, except when that would produce an inconsistency, in which case the CC is accommodated to the local context of the operator. While it is conceivable for the meaning of the operator to systematically interact with the possibility of local accommodation, no such interaction has been spelled out.
	%
	The second reason is that many contemporary analyses do not make predictions for the projection of the CC of many of the 20 predicates, as they are limited to (semi-)factive predicates (e.g., \citealt{heim_projection_1983,van_der_sandt_presupposition_1992}, whose CCs are analyzed as presuppositions) and or entailed CCs that project unless at-issue with respect to the Question Under Discussion (e.g., \citealt{abrusan_predicting_2011,simons_best_2017}). A possible exception is the analysis of \citealt{schlenker_triggering_2021}, which predicts the potential for projection for CCs that are contextually entailed. In the full talk, we discuss how this analysis might be able to capture the gradient projection observed in our experiment.
	%
	The third reason is that contemporary projection analyses do not make sufficiently fine-grained distinctions between different clause-embedding predicates (but only between whether the CC is a presupposition or entailed). Consequently, they do not make predictions about the by-predicate variation in the effect of operator on projection.

% \noindent {\bf Discussion:  Empirical implications and lexical properties.}
	%
	% {\bf THIS IS OLD, FROM ABOVE: So far, there has been no experimental investigation of by-operator variation comparing factive and semi-factive predicates. However, \citet{djarv_cognitive_2018} and \citet{tonhauser_how_2018} observed by-predicate variation in polar questions. \citet{djarv_cognitive_2018}, assessing acceptability of affirming the main clause while denying the CC, found higher ratings for \emph{be happy} and \emph{appreciate} (assumed to be factive) and \emph{be aware} than \emph{realize} (assumed to be semi-factive). Here, it is also not obvious how exactly this task relates to projection. \citet{tonhauser_how_2018} measured projection of the CC of a broad range of attitude predicates more directly, collecting ratings about speaker certainty about the CC. The observed differences did not match the expectations from Karttunen's classification (e.g., the CC of semi-factive \emph{realize} was as projective as that of factive \emph{be annoyed} and more than that of semi-factive \emph{discover}).}
	%
	Our results further question the proposed difference between factive and semi-factive predicates (see also \citealp{beaver_have_2010}).
	Future research appealing to these categories must clarify their definition. Additionally, claims about projection variability must be relativized to the entailment-canceling operator.
	% Although our data replicate the result from \citet{tonhauser_how_2018} that, in polar questions, the CC of \emph{discover} is less projective than that of \emph{know}, the same does not hold in conditionals.
	%
	Finally, our results provide further support (from negation, modals, and conditionals) for the result of \citet{degen_are_2022}, that projection does not categorically differentiate between (semi-)factive and non-factive predicates: The CCs of \emph{inform} and \emph{acknowledge}, for instance, are at least as projective as that of some (semi-)factive predicates.
	%
	% Further, the variability we found is gradient, confirming previous research that by-predicate variability is not determined by categorical lexical classes (\citealt{tonhauser_how_2018,degen_are_2022}),
	% and extending this result to by-predicate variability in interaction with entailment-cancelling contexts.
	%
	In spite of a lack of categorical distinctions about the projection behavior of our verbs, we can find some interesting initial generalizations over lexical properties, indicated in \textbf{Figure\ 2}.

@@

\newpage
{\scriptsize
\noindent {\bf (Selected) References:}
%
{\bf Beaver (2010).} Have you noticed that your belly button lint colour is related to the colour of your clothing? {\em Presuppositions and Discourse: Essays offered to Hans Kamp.}~\textbullet~
{\bf Degen \& Tonhauser (2022).} Are there factive predicates? An empirical investigation. {\em Language.}~\textbullet~
{\bf Djärv \& Bacovcin (2017).} Prosodic effects on factive presupposition projection. {\em Semantics and Linguistic Theory.}~\textbullet~
{\bf Djärv, Zehr \& Schwarz (2018).} Cognitive vs. emotive factives: An experimental differentiation. {\em Proceedings of Sinn und Bedeutung.}~\textbullet~
% {\bf Hooper \& Thompson (1973).} On the applicability of root transformations. {\em Linguistic Inquiry.} ~\textbullet~
{\bf Karttunen (1971).} Some observations on factivity. {\em Research on Language \& Social Interaction.} ~\textbullet~
{\bf Mahler (2020).} The social component of projection behavior of clausal complements. {\em Linguistic Society of America.}~\textbullet~
{\bf Smith and Hall (2014).} The relationship between projection and embedding environment. {\em Proceedings of the 48th Meeting of the Chicago Linguistics Society.}~\textbullet~
{\bf Tonhauser, Beaver, \& Degen (2018).} How projective is projective content? Gradience in projectivity and at-issueness. {\em Journal of Semantics.}~\textbullet~
% {\bf Tönnis (2021).} {\em German es-clefts in discourse. A question-based analysis involving expectedness.} Doctoral dissertation, Graz University.
% {\bf Zimmermann (2011).} {\em The grammatical expression of focus in West Chadic: Variation and uniformity in and across languages.} Walter de Gruyter.

@@

\begin{table}[h]
	\vspace{-1\baselineskip}\phantom{.}
	\centering
	\hspace{-1.2em}
	\begin{tabular}{p{.663\linewidth} p{.3\linewidth}}
		\scalebox{.77}{
			\begin{tabular}{llrrrr}
				Model & & Estimate & Std. Error & t-value\\
				\midrule
				\#1 & Intercept: \emph{question} & 0.52 & 0.01 & 87.31 & ***\\
				& operator: conditional & 0.04 & 0.01 & 5.07 & ***\\
				& operator: modal & -0.04 & 0.01 & -4.55 & ***\\
				& operator: negation & -0.03 & 0.01 & -4.30 & ***\\
				\midrule
				\#2 & Intercept: \emph{\bf be annoyed}/negation & 0.87 & 0.01 & 79.86 & ***\\
				& operator: conditional & -0.12 & 0.02  & -7.36 & ***\\
				& operator: modal & -0.16 & 0.02  & -10.01 & ***\\
				& operator: question & 0.02 & 0.01 & 1.72 & n.s.\\
				\midrule
				\#3 & Intercept: \emph{\bf discover}/negation & 0.68 & 0.01 & 62.70 & ***\\
				& operator: conditional & 0.11 & 0.02 & 7.11 & ***\\
				& operator: modal & -0.06 & 0.02 & -3.63 & ***\\
				& operator: question & 0.10 & 0.01 & 7.08 & ***\\
				\midrule
				\#4 & Intercept: \emph{\bf know}/negation & 0.79 & 0.01 & 72.97 & ***\\
				& operator: conditional & 0.00 & 0.02 & -0.06 & n.s.\\
				& operator: modal & -0.14 & 0.02 & -9.18 & ***\\
				& operator: question & 0.08 & 0.01 & 5.67 & ***\\
				\bottomrule
			\end{tabular}
		}
		&
		\parbox{\linewidth}{\caption{\small Excerpt of the output from three linear mixed effects models; \textbf{\#1} has fixed effects of operator; random effect: participant intercepts, \textbf{\#2-4} have fixed effect: operator, predicate, and their interaction; random effect: participant intercepts.
		Models were fit with \texttt{lme4, lmertest} in \texttt{R}. All three models also had at least $34$ highly significant interaction terms of \texttt{operator} and \texttt{predicate} with $p < 0.001$ (Not shown here).}\label{t:models}}

>>>>

\vspace{-.8\baselineskip}
\noindent 
	We present experimental evidence that the projection of the content of attitude complements \textbf{(i)} varies between entailment-canceling operators, and \textbf{(ii)} that this by-operator variation differs between attitude predicates.
	%
	The observed variability is not captured by existing theoretical accounts of projection
	(e.g., \citealt{heim_projection_1983,van_der_sandt_presupposition_1992,abrusan_predicting_2011,schlenker_triggering_2021}).
	%
	Our results suggest that an analysis must consider interactions between predicates and operators and raise important questions for future research on projection.

\noindent {\bf Projection across entailment-cancelling operators.}
	Language users may infer that a speaker who utters an attitude ascription, as in \ref{ex:family}, is committed to the content of the complement (CC, here: \emph{Julian dances salsa,})
	even when it occurs under an entailment-canceling operator, like negation \ref{ex:neg}, polar questions \ref{ex:q}, modals \ref{ex:mod}, or conditionals \ref{ex:cond}, in which case we say that it \emph{projects}.

@@

	\vspace{-.5\baselineskip}
	\noindent  Current research rarely examines projection variability across these operators, with conflicting findings.
	%
	\citet{karttunen_observations_1971} proposed a distinction between English factive predicates (e.g., \emph{be annoyed, regret}), where the CC projects across all four operators, and semi-factives (e.g., \emph{discover, realize, see, notice}) where it always projects across negation, but not always for the other operators.
	%
	Comparing different types of contents, \citet{smith_relationship_2014} found that the projective content of epithets and the CC of \emph{know} was more projective under negation than conditionals,
	whereas that of non-restrictive relative clauses and \emph{win} showed the opposite pattern.
	%
	This result was replicated for German \emph{wissen} `know' in \posscite{sieker_projective_2022} study on German attitude predicates, but as part of an overall pattern of higher projection ratings with negation than other operators. They found no interaction with predicate type, or evidence for the distinction of factives vs. semi-factives.

	These studies raise the question if the divergent results are due to cross-linguistic variation, task differences, or different contents being tested. To address this, we conducted a series of experiments designed to assess projection across the four entailment-canceling operators in \ref{ex:family}. We used the same projection measure as \citet{sieker_projective_2022} (the `certain that' diagnostic; see e.g., \citealp{tonhauser_how_2018,djarv_prosodic_2017,mahler_social_2020}) and applied it to the CC of 20 English clause-embedding predicates, including factive (\emph{be annoyed, know, reveal}) and semi-factive predicates (\emph{discover, see}),
	and 15 non-factive predicates, given recent findings that their complements may also project, albeit to varying degrees (\citealt{degen_are_2022}).

@@

\noindent
{\bf Results and Analysis.}
	Our analysis reveals two key results: \textbf{(i)} There is projection variability by operator. Mean projection ratings were higher under question-embeddings (Maximum likelihood estimate: $0.51$) than under negation (MLE: $0.48$) and modals ($0.47$), but lower than in conditional antecedents ($0.56$, see model \#1 in Table\ \ref{t:models}).
	%
	This result differs from that of \cite{sieker_projective_2022}, who observed that the CC of German attitude predicates projects more from under negation than the other operators.
	%
	\textbf{(ii)} There is by-predicate variation in the effect of operator on projection. This is illustrated in Figure~\ref{fig:figure1}, which shows mean projection ratings for the 20 attitude predicates by operator; predicates are ordered by their mean rating across all operators (\emph{be annoyed} has the highest overall mean).
	%
	For instance, the CC of \emph{be annoyed} projects more from under negation and questions than conditionals and modals, and the CC of \emph{discover} projects less from negation than conditionals and questions, and more from under negation than modals. The CC of \emph{know} projects less from under negation than questions, but more from under negation than modals, while the difference between negation and conditionals is not significant.
	%
	These generalizations are supported by models\ \# 2--4 in Table\ \ref{t:models}, which also each have at least $34$ highly significant interaction terms (out of $57$ possible interactions of operator and predicate).
	%
	%
	This result that by-operator projection variability interacts with predicate concurs with \citet{smith_relationship_2014}, while we did not reproduce their result that the CC of \emph{know} projects more from negation than conditionals. This differs from the result of \citet{sieker_projective_2022}, who found no interaction between predicates and operators.
	%
	Given that the methods and the set of projective contents of our experiment were very similar to theirs, this difference may suggest cross-linguistic variation in projection variability (cf. \citealt{tonhauser_projection_2020}).
	%
	On the other hand, in line with \citet{sieker_projective_2022}, our results are contrary to what would be expected based on \posscite{karttunen_observations_1971} distinction between factive and semi-factive predicates: The CC of (factive) \emph{be annoyed} does not project invariably from all four operators, and the CC of \emph{discover,}  which is considered semi-factive, does not project more from under negation than the other three operators. The pattern observed for {\em know} does not fit into either category.
	%

	%

@@

\noindent {\bf Discussion.}
	Our results---that projection is modulated by entailment-canceling operators and that there is by-predicate variation in the effect of operator on projection---are not captured by contemporary projection analyses, for several reasons.
	%
	The first is that contemporary analyses do not lead us to expect interactions with different types of entailment-cancelling operators. In \citet{heim_projection_1983}, for instance, the CC of (semi-)factive predicates projects to the global context, except when that would produce an inconsistency, in which case the CC is accommodated to the local context of the operator. While it is conceivable for the meaning of the operator to systematically interact with the possibility of local accommodation, no such interaction has been spelled out.
	%
	The second reason is that many contemporary analyses do not make predictions for the projection of the CC of many of the 20 predicates, as they are limited to (semi-)factive predicates, whose CCs are analyzed as presuppositions (e.g., \citealt{heim_projection_1983,van_der_sandt_presupposition_1992}), or entailed CCs that project unless at-issue with respect to the Question Under Discussion (e.g., \citealt{abrusan_predicting_2011,simons_best_2017}). A possible exception is the analysis of \citealt{schlenker_triggering_2021}, which predicts the potential for projection for CCs that are contextually entailed. In a full talk, we would like to discuss how this analysis might be extended to capture the gradient projection observed in our experiment.
	%
	The third reason is that contemporary projection analyses do not make sufficiently fine-grained distinctions between different clause-embedding predicates (but only between whether the CC is a presupposition or entailed). Consequently, they do not make predictions about the by-predicate variation in the effect of operator on projection.

% \noindent {\bf Discussion:  Empirical implications and lexical properties.}
	%
	Our results further question \posscite{karttunen_observations_1971} proposed difference between factive and semi-factive predicates (see also \citealt{beaver_have_2010}).
	Future research appealing to these categories must clarify their definition. Additionally, claims about projection variability must be relativized to the entailment-canceling operator.
	% Although our data replicate the result from \citet{tonhauser_how_2018} that, in polar questions, the CC of \emph{discover} is less projective than that of \emph{know}, the same does not hold in conditionals.
	%
	Finally, our results provide further support (from negation, modals, and conditionals) for the result of \citet{degen_are_2022}, that projection does not categorically differentiate between (semi-)factive and non-factive predicates: The CCs of \emph{inform} and \emph{acknowledge}, for instance, are at least as projective as that of some (semi-)factive predicates.
	%
	% Further, the variability we found is gradient, confirming previous research that by-predicate variability is not determined by categorical lexical classes (\citealt{tonhauser_how_2018,degen_are_2022}),
	% and extending this result to by-predicate variability in interaction with entailment-cancelling contexts.
	%
	In spite of a lack of categorical distinctions about the projection behavior of our verbs, we can find some interesting initial generalizations over lexical properties, indicated in \textbf{Figure\ 2}.

@@

\newpage
{\scriptsize
\noindent {\bf (Selected) References:}
%
{\bf Abrusán (2011).} Predicting the presuppositions of soft triggers. {\em Linguistics and philosophy.} ~\textbullet~
% {\bf Beaver (2010).} Have you noticed that your belly button lint colour is related to the colour of your clothing? {\em Presuppositions and Discourse: Essays offered to Hans Kamp.}~\textbullet~
{\bf Degen \& Tonhauser (2022).} Are there factive predicates? An empirical investigation. {\em Language.}~\textbullet~
{\bf Djärv \& Bacovcin (2017).} Prosodic effects on factive presupposition projection. {\em Semantics and Linguistic Theory.}~\textbullet~
% {\bf Djärv, Zehr \& Schwarz (2018).} Cognitive vs. emotive factives: An experimental differentiation. {\em Proceedings of Sinn und Bedeutung.}~\textbullet~
{\bf Heim (1983).} On the Projection Problem for Presuppositions. {\em Proceedings of the Second West Coast Conference on Formal Linguistics.}~\textbullet~
% {\bf Hooper \& Thompson (1973).} On the applicability of root transformations. {\em Linguistic Inquiry.} ~\textbullet~
{\bf Karttunen (1971).} Some observations on factivity. {\em Research on Language \& Social Interaction.} ~\textbullet~
% {\bf Mahler (2020).} The social component of projection behavior of clausal complements. {\em Linguistic Society of America.}~\textbullet~
% {\bf van der Sandt (1992).} Presupposition projection as anaphora resolution. {\em Journal of Semantics.}~\textbullet~
{\bf Schlenker (2021).} Triggering presuppositions. {\em Glossa: A Journal of General Linguistics.}~\textbullet~
{\bf Sieker \& Solstad (2022).} Projective variability of (semi) factive verbs in family of sentence contexts: A rating study. {\em Proceedings of the 23rd Amsterdam Colloquium.}~\textbullet~
% {\bf Simons, Beaver, Roberts \& Tonhauser (2017).} The best question: Explaining the projection behavior of factives. {\em Discourse processes.}~\textbullet~
{\bf Smith and Hall (2014).} The relationship between projection and embedding environment. {\em Proceedings of the 48th Meeting of the Chicago Linguistics Society.}~\textbullet~
{\bf Tonhauser (2020).} Projection variability in Paraguayan Guaraní. {\em Natural Language \& Linguistic Theory.}~\textbullet~
{\bf Tonhauser, Beaver, \& Degen (2018).} How projective is projective content? Gradience in projectivity and at-issueness. {\em Journal of Semantics.}
% {\bf Tönnis (2021).} {\em German es-clefts in discourse. A question-based analysis involving expectedness.} Doctoral dissertation, Graz University.
% {\bf Zimmermann (2011).} {\em The grammatical expression of focus in West Chadic: Variation and uniformity in and across languages.} Walter de Gruyter.

@@

\begin{table}[h]
	\vspace{-1\baselineskip}\phantom{.}
	\centering
	\hspace{-1.3em}
	\begin{tabular}{p{.65\linewidth} p{.31\linewidth}}
		\scalebox{.75}{
			\begin{tabular}{llrrrr}
				Model & & Estimate & Std. Error & t-value\\
				\midrule
				\#1 & Intercept: \emph{question} & 0.51 & 0.01 & 44.78 & ***\\
				& operator: conditional & 0.05 & 0.01 & 5.30 & ***\\
				& operator: modal & -0.04 & 0.01 & -4.45 & ***\\
				& operator: negation & -0.03 & 0.01 & -4.67 & ***\\
				\midrule
				\#2 & Intercept: \emph{\bf be annoyed}/negation & 0.87 & 0.01 & 79.86 & ***\\
				& operator: conditional & -0.12 & 0.02  & -7.36 & ***\\
				& operator: modal & -0.16 & 0.02  & -10.01 & ***\\
				& operator: question & 0.02 & 0.01 & 1.72 & n.s.\\
				\midrule
				\#3 & Intercept: \emph{\bf discover}/negation & 0.68 & 0.01 & 62.70 & ***\\
				& operator: conditional & 0.11 & 0.02 & 7.11 & ***\\
				& operator: modal & -0.06 & 0.02 & -3.63 & ***\\
				& operator: question & 0.10 & 0.01 & 7.08 & ***\\
				\midrule
				\#4 & Intercept: \emph{\bf know}/negation & 0.79 & 0.01 & 72.97 & ***\\
				& operator: conditional & 0.00 & 0.02 & -0.06 & n.s.\\
				& operator: modal & -0.14 & 0.02 & -9.18 & ***\\
				& operator: question & 0.08 & 0.01 & 5.67 & ***\\
				\bottomrule
			\end{tabular}
		}
		&
		\parbox{\linewidth}{\caption{\small Excerpt of the output from three linear mixed effects models; \textbf{\#1} has fixed effects of operator; random effects: participant and item intercepts, \textbf{\#2-4} have fixed effect: operator, predicate, and their interaction; random effect: participant intercepts.
		Models were fit with \texttt{lme4, lmertest} in \texttt{R}. Models \textbf{\#2--4} also had at least $34$ highly significant interaction terms of \texttt{operator} and \texttt{predicate} with $p < 0.001$ (not shown here).}\label{t:models}}
